\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-28 paper/experiments.tex
paper: fix experiment todo

\subsection{Data sets} \label{subsec:datasets}
We collected three data sets our experiments.
For all data sets, we selected a subset of the original attributes.
We also enumerated strings and encoded them with an appropriate integer value.
\todo{describe all data transformations. jose?}

>>>>

\subsection{Data sets}\label{subsec:datasets}
We collected three data sets our experiments.
For all data sets, we selected a subset of the original attributes.
We also transformed all data values to an integer representation by enumerating strings and transforming floating point values into an appropriate range.
